---
title: "`r paste('Life Expectancy in ', params$country)`"
author: "Agnes and Teteh"
date: "`r format(Sys.Date(), '%A %b %Y')`"
output: 
  html_document:
    theme: readable
    highlight: haddock
    number_sections: TRUE
    toc: TRUE
    toc_depth: 1
params:
  country: Cambodia
  continent: Asia
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r Libraries, echo = FALSE, message = FALSE, warning = FALSE}

# install.packages("tidyverse")
library(tidyverse)

# install.packages("kableExtra")
library(kableExtra)

# install.packages("gapminder")
library(gapminder)

# install.packages("leaflet")
library(leaflet)

library(shiny)
```

```{r Data Preparation}

# Country of Interest
gapminder_country <- gapminder %>%
  filter(country == params$country,
         year > 1980 & year <= 2010)

# Wider Continent

gapminder_continent <- gapminder %>%
  filter(continent == params$continent,
         year > 1980 & year <= 2010)

# Whole world
gapminder_sub <- gapminder %>%
  filter(year > 1980 & year <= 2010)

```


# Life expectancy in `r params$country`
## 2nd level
### 3rd level

```{r lifeExp-plot, fig.align = 'right'}

ggplot() +
  geom_line(
    data = gapminder_sub,
    aes(
      x = year,
      y = lifeExp,
      group = country,
      color = continent
    ),
    alpha = 0.2,
    lwd = 0.75
  ) +
  geom_line(
    data = gapminder_country,
    aes(x = year,
        y = lifeExp,
        color = continent
    ),
    lwd = 2
    ) +
  labs(
    x = "Year",
    y = "Life Expectancy",
    title = paste(
      "Life Expectancy over time in",
      params$country,
      "from 1980 to 2010",
      sep = " "
    ),
    color = "Continent"
  ) +
  geom_label(
    data = gapminder_country %>%
      slice(which.min(year)),
    aes(
      x = year, 
      y = lifeExp, 
      label = country
    ),
    nudge_x = 2,
    nudge_y = -2.5
  )

```


```{r min_lifeExp}

min_lifeExp <- gapminder_country %>%
  summarise(min_lifeExp = round(min(lifeExp), 2))

```


```{r average_lifeExp}

average_lifeExp <- gapminder_country %>%
  summarise(average_lifeExp = round(mean(lifeExp), 2))

```


The average life expectancy in `r params$country` between 1980 and 2010 was `r average_lifeExp`. 

The minimum life expectancy in `r params$country` between 1980 and 2010 was `r min_lifeExp`.

# Life expectancy in the `r params$continent`


```{r table}

lifeExp_country <- gapminder_continent %>%
  group_by(country) %>%
  summarise(mean_lifeExp = mean(lifeExp))

lifeExp_country %>% 
  kable(booktabs = T,
        caption = paste0("Mean Life Expectancy in " , params$continent)) %>%
  kable_styling() %>%
  row_spec(which(lifeExp_country$country == params$country), bold = T, color = "white", background = "blue")

```

# Leaflet map

```{r}

df = data.frame(Lat = 1:10, Long = rnorm(10))
leaflet(df) %>% 
  addCircles() %>%
  addProviderTiles(providers$CartoDB.Positron)

```


## About the data

The data comes from the [gapminder](http://www.gapminder.org/data/)
dataset from the [gapminder package](https://github.com/jennybc/gapminder) by Jenny Bryan.
