---
title: "Reproducible Country Report"
author: "Agnes and Teteh"
date: "30/07/2020"
output:
  html_document:
    df_print: paged
  highlight: haddock
  number_sections: yes
  toc: yes
  theme: cosmo
params:
  country: Japan
  continent: Asia
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE) # Step 2 Changing the code chunk settings
```


```{r Libraries}

# install.packages("tidyverse")
library(tidyverse)

# install.packages("kableExtra")
library(kableExtra)

# install.packages("gapminder")
library(gapminder)

```

```{r Data Preparation}

# Country of Interest
gapminder_country <- gapminder %>%
  filter(country == params$country,
         year > 1980 & year <= 2010)

# Wider Continent

gapminder_continent <- gapminder %>%
  filter(continent == params$continent, # Step 4. Update Americas with the parameter for continent
         year > 1980 & year <= 2010)

# Whole world
gapminder_sub <- gapminder %>%
  filter(year > 1980 & year <= 2010)

```


# Life expectancy in `r params$country`


```{r lifeExp-plot}

ggplot() +
  geom_line(
    data = gapminder_sub,
    aes(
      x = year,
      y = lifeExp,
      group = country,
      color = continent
    ),
    alpha = 0.2,
    lwd = 0.75
  ) +
  geom_line(
    data = gapminder_country,
    aes(x = year,
        y = lifeExp,
        color = continent
    ),
    lwd = 2
    ) +
  labs(
    x = "Year",
    y = "Life Expectancy",
    title = paste(
      "Life Expectancy over time in",
      params$country,
      "from 1980 to 2010",
      sep = " "
    ),
    color = "Continent"
  ) +
  geom_label(
    data = gapminder_country %>%
      slice(which.min(year)),
    aes(
      x = year, 
      y = lifeExp, 
      label = country
    ),
    nudge_x = 2,
    nudge_y = -2.5
  )

```


```{r average_lifeExp}

average_lifeExp <- gapminder_country %>%
  summarise(average_lifeExp = round(mean(lifeExp), 2))

```

```{r min_lifeExp}

## Step 3 Calculating another summary statistic

min_lifeExp <- gapminder_country %>%
  summarise(min_lifeExp = round(min(lifeExp), 2))

```

```{r max_lifeExp}

## Step 3 Calculating another summary statistic

max_lifeExp <- gapminder_country %>%
  summarise(max_lifeExp = round(max(lifeExp), 2))

```

The average life expectancy in `r params$country` between 1980 and 2010 was `r average_lifeExp`. The minimum life expectancy in `r params$country` between 1980 and 2010 was `r min_lifeExp`. The maximum life expectancy in `r params$country` between 1980 and 2010 was `r max_lifeExp`. 

<!-- Step 4. Replace Americas with the new parameter for continent -->

# Life expectancy in the `r params$continent` 

```{r}

lifeExp_country <- gapminder_continent %>%
  group_by(country) %>%
  summarise(mean_lifeExp = mean(lifeExp))

lifeExp_country %>% 
  kable(booktabs = T,
        caption = paste("Mean Life Expectancy in the", params$continent, sep = " ")) %>% # Step 4 Replace mentions of Americas with the parameter for continent.
  kable_styling() %>%
  row_spec(which(lifeExp_country$country == params$country), bold = T, color = "white", background = "blue")

```



<!-- Step 2 Adding a link and a reference -->

### About the data

The data comes from the [gapminder](http://www.gapminder.org/data/) dataset from the [`gapminder` package](https://github.com/jennybc/gapminder) by Jenny Bryan.